testibng

### 2024-01-06 R FIle.qmd
testing

```{r}
house <- house |>
  mutate(state = str_to_sentence(state)) |> # change from all caps to sentence case
```

@@

```{r}
states |> 
  ggplot(aes(x = year, y = p_covered, color = state)) +
  geom_point()
```

```{r}
house <- house |>
  mutate(state = str_to_sentence(state))
```

```{r}
states |> 
  filter(sector == "Total") |> 
  left_join(house, by = c("year", "state")) |> 
  filter(party == "DEMOCRAT" | party == "REPUBLICAN") |> 
  filter(year > 2012) |> 
  ggplot(aes(x = party, y = p_members)) +
  geom_boxplot()
```

```{r}
test <- states |> 
  filter(sector == "Total") |> 
  left_join(house, by = c("year", "state")) |> 
  filter(party == "DEMOCRAT" | party == "REPUBLICAN") |> 
  filter(year > 2012)
```

```{r}
t.test(p_members ~ party, data = test, conf.level = .9)
```

>>>>

```{r}
house <- house |>
  mutate(state = str_to_sentence(state)) |>  # change from all caps to sentence case
  mutate(regions = state.region[match(state_po, state.abb)]) # add regions 
```

#### Combining house and states dataframes
The states data set has five entries for each year for each of the five `sectors`. For this project we will use the `total` sector. A decades column will also be added.

```{r}
full_data <- states |> 
  filter(sector == "Total") |> 
  left_join(house, by = c("year", "state")) |> 
  filter(party == "DEMOCRAT" | party == "REPUBLICAN") |> 
  mutate(decade = paste0((year - year %% 10), "s"),
         party_binary = ifelse(party == "DEMOCRAT", 0, 1)) 
```

@@

```{r}
full_data |> 
  ggplot(aes(x = year, y = p_covered, color = regions)) +
  geom_point() +
  geom_smooth()
```

```{r}
full_data |> 
  ggplot(aes(x = party, y = p_members)) +
  geom_boxplot() +
  facet_wrap(vars(decade))
```

```{r}
t.test(p_members ~ party, data = full_data, conf.level = .9)
```
```{r}
full_data_after_2008 <- full_data |> 
  filter(year > 2008)
t.test(p_members ~ party, data = full_data_after_2008, conf.level = .9)
```
## Modeling
```{r}
model <- glm(party_binary ~ p_members, family = "binomial", data = full_data)
summary(model)
```

## Conclusion
